Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-26 papers/intro_paper/appendix.tex
changes in Appendices

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines). The GR prediction for the frequency and damping time is indicated by the black cross. While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not. The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}. All signals are recovered using the $\pSEOB$ model.}
        \label{fig:21g_systematics}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}
As mentioned in the main text, for low-SNR events with negligible higher-modes and for which only the post-merger is detectable, there is a strong degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$. For those cases, only the reconstructed frequency and damping time $(f_{220},\tau _{220})$ can be independently measured from the data.

To justify this statement, in Fig.~\ref{fig:correlations} we show corner plots that illustrate the correlations between the non-GR parameters $(\df{220}, \dtau{220})$, the detector-frame total mass $M(1+z)$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an event for which both the pre- and post-merger phase are measurable, and for GW190521 (right panel), an event in which the post-merger has ${\rm SNR}> 8$ but the pre-merger has an SNR below 8. For GW190521, due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D posterior for $M(1+z)$ is pushed towards the upper boundary of its prior, despite the very wide prior employed in the analysis. This in turn renders the measurement of $\df{220}$ (and to a lesser degree of $\dtau{220}$) highly dependent on the upper boundary of the total mass prior. On the other hand, this issue does not significantly affect the posteriors for the reconstructed quantities $(f_{220},\tau _{220})$ which are well measured and nearly independent on the upper prior boundary for $M(1+z)$. 
%
This is to be contrasted with the results for GW150914. In this case, the extra information coming from the pre-merger phase allows to break the degeneracy between the non-GR parameters and the total mass, and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can be measured at the same time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{center}
        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$. The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
post-merger phase of the signal, whereas the right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase but not in the pre-merger phase.}
        \label{fig:correlations}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
        \caption{90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines). The GR prediction for the frequency and damping time is indicated by the black cross. While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not. The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}. All signals are recovered using the $\pSEOB$ model.}
        \label{fig:21g_systematics}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}

As mentioned in the main text, for low-SNR events with negligible
higher-modes and for which only the post-merger is detectable, there
is a strong degeneracy between the binary's total mass and the non-GR
deviations $(\df{220}, \dtau{220})$. For those cases, only the
reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
be independently measured from the data.

To justify this statement, in Fig.~\ref{fig:correlations} we show
corner plots that illustrate the correlations between the non-GR
parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
$M(1+z)$ and the reconstructed frequency and damping time
$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
event for which both the pre- and post-merger phase are measurable,
and for GW190521 (right panel), an event in which the post-merger has
${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
posterior for $M(1+z)$ is pushed towards the upper boundary of its
prior, despite the very wide prior employed in the analysis. This in
turn renders the measurement of $\df{220}$ (and to a lesser degree of
$\dtau{220}$) highly dependent on the upper boundary of the total mass
prior. On the other hand, this issue does not significantly affect the
posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
which are well measured and nearly independent on the upper prior
boundary for $M(1+z)$.
%
This is to be contrasted with the results for GW150914. In this case, 
the extra information coming from the pre-merger phase allows to break 
the degeneracy between the non-GR parameters and the total mass, 
and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
be measured at the same time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{center}
        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$. The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
post-merger phase of the signal, and the correlations are absent. The right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase, but not in the pre-merger phase, and the correlations are present.}
        \label{fig:correlations}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
